\subsubsection{Overview}


This section is about the SmartAlvarTagDetection Component. The component is used to identify the Alvar Tags on the MPS machines, which is required for the exploration phase where the robots have to explore the game field and find MPS machines and identify the MPS based on their Alvar Tag. \\

Each MPS has their own Alvar Tag, one in the front and one in the back of the machine. This is important for the production phase later. On the field there are seven machines for each team. There are four types of MPS Machines, Base station, Cap station, Ring station and Storage station. All together there are 14 machines with 28 Alvar Tags. \\
Bild von Alvar Tag auf einer MPS. \\

The main idea is that the SmartAlvarTagDetection component identifies the tags. To do so, the component uses an algorithm to determine the Alvar Tag. Therefore, the component needs a picture of the Tag which is taken by a webcam mounted on each of the robotinos and operated by the SmartUnicapImageServer. The SmartAlvarTagDetection components is only one out of many components that are operated and instructed by the InstructionPlanner via the Sequencer (LISPServer). \\
Explain how to operate SmartAlvarTagDetection and SmartUnicapImageServer with DeploymentAlvarTagTest

\subsubsection{CommObjects}

This section describes the CommObjects that are used to communicate with the InstructionPlanner and other componentes.

\subsubsection{Previous State}

The previous team already had an implementation of the SmartAlvarTagDetection. In their version, they only had implemented the algorithm to scan pictures and identify whether there is a tag or not. They could not communicate with other components or the InstructionPlanner. \\

Bild von Algorithm \\

Explain Algorithm


\subsubsection{Current State}

The current version, which was used in the 2017 RoboCup German Open Logistics Leauge in Magdeburg, is able to identify the tags, communicate with the InstructionPlanner via the LISP Server and has some sort of error handling. When the SmartAlvarTagDetection returns the message, that no tag was found, the InstructionPlanner keeps triggering the component five times and if it still sends no tag was found, one can be sure that there really is no tag and it is not a problem with the algorithm or bad picture quality. 
